% Created 2020-04-11 Sat 03:29
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Michiel van Oosten}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Michiel van Oosten},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

Dear reader,

I am a Dutchman who has been living in Australia since 1994.

I am self-taught in both programming and piano. I began programming in my early
teens and started playing piano at nineteen. I finished a conservatorium
education in Australia in my mid twenties. Programming has been an undercurrent
throughout my whole life, and after having explored music for some time I
focused on programming since about 2012-13.

I hope to bring thoroughness, ideas and architectural (and artistic) insight to
a team and projects. I enjoy designing and thinking about long term design and
implementation of these designs.

My coding environment: laptop running Linux (Ubuntu), i3wm, Emacs and
Chrome/Firefox, my own tools. All my code is on \href{http://github.com/michieljoris}{github}. A guide is on my site at
\emph{\href{https://www.axion5.net/my-github.html}{axion5.net/my-github.html}}.

Some more background info:

\begin{itemize}
\item I went to VWO (Science preparatory school), courses in maths, history and philosophy at Universities of Leiden and Amsterdam. Degree in piano at Brisbane Griffith Conservatorium.
\item Favorite language is lisp after working through TEOCS in Common Lisp.
\item Wrote my own server, build and module system. It does for me what most people use Express, Grunt/Gulp/Brunch and Browserify for.
\item Java and C++ put me thoroughly off OOP. Functional approach is better.
\item Studying CS curriculum when time allows (SICP will be finished one day)
\item Working knowledge of html and css (and sass and less etc), but not overly fond of it.
\item Would love to write in and learn more about Haskell and Erlang, but also D, Rust and Julia.
\item Dream project: write Lisp operating system..
\item Major long term interest: computer systems' software reliability, robustness. Ultimately
software should be somehow self repairing, self-reliant and with built-in
redundancy, and as a whole extremely fault tolerant.
\end{itemize}

Some more background info is on \href{http://careers.stackoverflow.com/michieljoris}{careers.stackoverflow} and \href{http://nl.linkedin.com/in/michieljoris/}{linkedin}.
\end{document}
