% Created 2014-10-25 za 00:34
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\providecommand{\alert}[1]{\textbf{#1}}

\title{Dear reader,}
\author{michieljoris}
\date{\today}

\begin{document}

\maketitle


I would like to ask for you to consider this cover letter somewhat more
carefully than you would normally. As you can see on the attached CV I have not
so many programming credentials to my name as you would normally see. Why it
might still be interesting for us to got get in contact is because of the
following:

\begin{itemize}
\item Despite not having a formal CS education I might still have enough coding
  chops to be of help to you. I am a self-taught programmer as I am a
  self-taught pianist. I finished a conservatorium degree without previous piano
  lessons, this still amazes me really. I have been at least as thorough, and
  still am, in educating myself in programming. I have been programming on and
  off since I was 13 years old. Piano and music was just an enormous challenge
  when I was 19 and diverted me in some sense from the direction I always was
  going to go anyway. See following point:
\item I went to VWO (Science preparatory school), then started a maths degree in
  Leiden (then philosophy, picked up piano, then history, and finally piano).
\item I have a thorough knowledge of javascript, having written it for a couple of
  years now. See my \href{http://github.com/michieljoris}{github} account.
\item Since learning of lisp it's my favorite language, however web apps are written
  in javascript. Maybe not anymore now. I'm switching to ClojureScript.
\item To prove to myself I can write javascript I wrote my own server, build and
  module system. It does for me what most people use Express, Grunt and
  Browserify for.
\item I'm familiar with and/or knowledgeable of most current
  libs/trends/frameworks/languages.
\item Not fond of OOPS, prefer functional approach, I write javascript in a
  functional as much I can, avoiding \emph{this} wherever I can..
\item Plans and ideas for multiple apps/utilities.
\item Studying CS curriculum when time allows
\item Interested in web apps, not so much web sites, and any technology that will
  make web apps easier to make, front and backend.
\item Working knowledge of html and css (and sass and less etc), but not overly fond of it.
\item Would love the opportunity to work with any of the more modern languages such
  as Haskell, Julia, D, Rust, Go, Clojure and Scala, but sticking with
  Javascript for now for reasons of marketability.
\item Dream project: write Lisp operating system..
\item Main interest: computer systems' software reliability, robustness. Ultimately
  software should be somehow self repairing, self-reliant and with built-in
  redundancy, and as a whole extremely fault tolerant.
\item I even keep a \href{http://www.axion5.net}{blog}!!
\end{itemize}
  
I believe the future is in the web as far as apps are concerned. I'm looking for
similar minded people interested in building these using the best languages, the
smartest libraries and cleverest implementations resulting in fast deployment
and quick iteration. I am interested in learning and applying anything to
further that goal. See also my \href{http://github.com/michieljoris/cape}{cape} project.

Interests beyond web applications are distributed programming, operating
systems, compilers but foremost robustness, reliability and ease of use of
computer systems. A computer shouldn't fail but it does so often.

Some more background info is on \href{http://careers.stackoverflow.com/michieljoris}{careers.stackoverflow}.

Kind regards,

Michiel van Oosten

\end{document}
